Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-17 appendix.qmd
Updated Figure 2

```{r}
library(ggplot2)
library(dplyr)
library(quollr)
library(readr)
library(ggforce)
library(patchwork)
library(kableExtra)

@@

emb_df2 <- tibble(emb1 = 0.161, emb2 = 0.7395) |>
  add_row(emb1 = 0.683, emb2 = 0.7395) |>
  add_row(emb1 = 0.2915, emb2 = 0.965) |>
  add_row(emb1 = 0.5525, emb2 = 0.965) |>
  add_row(emb1 = 0.2915, emb2 = 0.5135) |>
  add_row(emb1 = 0.5525, emb2 = 0.5135) |>
  add_row(emb1 = 0.422, emb2 = 1.04) |>
  add_row(emb1 = 0.161, emb2 = 0.890) |>
  add_row(emb1 = 0.161, emb2 = 0.589) |>
  add_row(emb1 = 0.422, emb2 = 0.438) |>
  add_row(emb1 = 0.683, emb2 = 0.589) |>
  add_row(emb1 = 0.683, emb2 = 0.890)

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = emb_df2, aes(x = emb1, y = emb2), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_segment(x = 0.161, y = 0.7395, xend = -0.06, yend = 0.740, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.683, y = 0.7395, xend = 0.45, yend = 0.740, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.2915, y = 0.965, xend = 0.43, yend = 0.79, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.5525, y = 0.965, xend = 0.44, yend = 0.8, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.2915, y = 0.5135, xend = 0.18, yend = 0.32, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.5525, y = 0.5135, xend = 0.67, yend = 0.32, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.422, y = 1.04, xend = 0.42, yend = 0.85, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.161, y = 0.890, xend = -0.02, yend = 0.8, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.161, y = 0.589, xend = 0.161, yend = 0.4, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.422, y = 0.438, xend = 0.25, yend = 0.3, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.683, y = 0.589, xend = 0.683, yend = 0.4, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.683, y = 0.890, xend = 0.5, yend = 0.82, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd")

>>>>

```{r}
library(ggplot2)
library(dplyr)
library(quollr)
library(readr)
library(ggforce)
library(patchwork)
library(kableExtra)
library(tidyr)

@@

hex_data <- hex_grid |> 
  dplyr::filter(hex_poly_id == 8)

# Create all pairs of rows
pairs <- expand_grid(row1 = 1:nrow(hex_data), row2 = 1:nrow(hex_data)) |>
  filter(row1 < row2)

# Compute middle points for each pair of rows
middle_points <- pairs |>
  rowwise() |>
  mutate(
    hex_poly_id = hex_data$hex_poly_id[row1],
    x = (hex_data$x[row1] + hex_data$x[row2]) / 2,
    y = (hex_data$y[row1] + hex_data$y[row2]) / 2
  ) |>
  ungroup() |>
  select(hex_poly_id, x, y) |>
  filter(row_number() %in% c(1, 5, 6, 10, 13, 15))

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = middle_points, aes(x = x, y = y), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_segment(x = 0.161, y = 0.7395, xend = -0.06, yend = 0.740, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.683, y = 0.7395, xend = 0.45, yend = 0.740, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.2915, y = 0.965, xend = 0.43, yend = 0.79, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.5525, y = 0.965, xend = 0.44, yend = 0.8, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.2915, y = 0.5135, xend = 0.18, yend = 0.32, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.5525, y = 0.5135, xend = 0.67, yend = 0.32, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.422, y = 1.04, xend = 0.42, yend = 0.85, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.161, y = 0.890, xend = -0.02, yend = 0.8, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.161, y = 0.589, xend = 0.161, yend = 0.4, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.422, y = 0.438, xend = 0.25, yend = 0.3, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.683, y = 0.589, xend = 0.683, yend = 0.4, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.683, y = 0.890, xend = 0.5, yend = 0.82, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd")
